Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-08-05 letters/reply_referee.tex

\setkomavar{fromname}{Dr. Elke Faßhauer}
\setkomavar{fromaddress}{Department of Chemistry\\University of Troms\o --- The Artic University of Norway\\9037 Tromsø\\Norway}
\setkomavar{fromphone}{+47 40382485}
\setkomavar{fromemail}{elke.fasshauer@uit.no}
\setkomavar{subject}{Revision of Out Article jp-2016-06665e}
\setkomavar{signature}{Dr. Elke Faßhauer (corresponding author)}

\begin{document}
\begin{letter}{To the Editor}

	\opening{Dear Editor,}

Our paper has been reviewed by two of your Referees,
who recommended it for the publication in the
New Journal of Physics subject to minor amendments.
We are thankful for the comments made by the Referees and
respond to them below. We additionally reply on two of the additional
format requests made by Ms. Maja Vujovic.

@@

 We have clarified the information in the figure caption by including the sentence: {\color{blue}{The dotted line shows the unscaled spectrum in this region.}}

 \item \emph{The colour schemes of some of the figures lead to confusion when printed in grayscale. Some effort could be made to resolve this.}\vspace{0.3cm}\\
       The reviewer does not specify which figures are affected by this.
       We therefore assume a reference to figures 4-8. In these, the
       information density is very high, especially within the stick spectrum.
       Due to this, overlapping dotted or dashed lines would not be
       decipherable and only confuse the reader not only on a grayscale print
       but also a coloured print. Since the majority of scientific journals
       at least have the pdf version available as well, we therefore leave
       the colour choice, which was made to allow readability by
       colour blind people as well.

\end{enumerate}

We also applied almost all requested changes to the format of the manuscript.
Request number 4 (remove unpublished results from References) asks for
published and sonn-to-be published material. Since the manuscript in
questions was submitted a month ago and was an invited contribution
for special issue to be published in October at the latest.
We expect this manuscript
will become published then. We also interpret this timeframe as soon
and therefore leave the Reference in the list.

For point 6 see Reviewer 2 point 5.

### 2016-08-05 theo_results.tex
last points
format

Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
%Both spectra show several smaller peaks which
%are convoluted into one single peak with a maximum at
%approximately \unit[0.2]{eV}. 
%In comparison to the 13 argon atoms core
%spectrum t
The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
signals at higher energies of the secondary electron. These features
can be explained by investigating the Ar-Xe distance distributions
in the clusters, shown
in the bottom panel of Figure \ref{figure:surf}. 
Every different value of the atom pair distance
results in a different energy of the secondary electron and only pairs
with a distance of larger than the channel opening distance
(dashed gray line) will contribute
to the spectrum. 
In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
The larger the interatomic distance, the higher is the
kinetic energy of the secondary electron for a given channel.
%Since the cluster with an Ar core of 55 atoms is larger, and therefore
%contains Ar-Xe pairs with larger distances, its spectrum 
Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
%energies as well.
This relation between ICD energy and cluster size holds true for all cluster structures.
%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.

@@

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence decrease the decay width. Since the folded peaks
are constituted from several pairs of different distances, it would result
in a slight peak shift to higher energies of the combined peak at lowest energy.

>>>>

Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
%Both spectra show several smaller peaks which
%are convoluted into one single peak with a maximum at
%approximately \unit[0.2]{eV}. 
%In comparison to the 13 argon atoms core
%spectrum t
The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
signals at higher energies of the secondary electron. These features
can be explained by investigating the Ar-Xe distance distributions
in the clusters, shown
in the lower panel of Figure \ref{figure:surf}. 
Every different value of the atom pair distance
results in a different energy of the secondary electron and only pairs
with a distance of larger than the channel opening distance
(dashed gray line) will contribute
to the spectrum. 
In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
The larger the interatomic distance, the higher is the
kinetic energy of the secondary electron for a given channel.
%Since the cluster with an Ar core of 55 atoms is larger, and therefore
%contains Ar-Xe pairs with larger distances, its spectrum 
Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
%energies as well.
This relation between ICD energy and cluster size holds true for all cluster structures.
%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.

@@

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence decrease the decay width. Since the folded peaks
are constituted from several pairs of different distances, it would result
in a slight peak shift to higher energies of the combined peak at lowest energy.
For a more detailed discussion of nculear dynamics for the ICD in dimers vs.
in clusters see Ref. \citenum{fasshauernjp}
